---
title: "Convert zooplankton abundances to biomass"
author: "A. Lindborg"
date: "5/9/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Purpose
Convert zooplankton control data from abundance to biomass, using recent length-weight information provided by GmbH.

## Steps
1) Determine biomass per individual
    - Use the "regression midpoints" values provided by Jurgen/GmBH, on the "Zooplankton" tab in the "Additional Parameters Mesocosm 211210_vs.xlsx" worksheet.
    - Assign each group it's length/weight (LW) value. 
    - If a specific species doesn't have LW values, assign the LW values of the closest proximity 
    
2) Convert effects data measurements from abundance (individuals/L) to biomass (g/m2 or g/L)
  
3) Sum the total biomass for the modeled group
    - For multi-species groups (e.g. Rotifers), determine biomass for each of the species (above step), but sum together for 1 group biomass value
  
# Documentation
Relevant files in the documentation folder calibration analyses:

"Email_Decision_on_Calibration_Biomass_Conversion_2021-12-10.pdf"
"Email_Updated_Length_Data_2021-12-10.pdf"

# History
5/9/2022 - A. Lindborg modifies script based on validation script of same name

# Setup
```{r setup}
library(tidyverse)
library(openxlsx)
library(janitor)
library(RColorBrewer)


options(scipen = 9999)
```

# Data
This analysis uses 3 data sets:

1. Individual weights for Zooplankton species
    - Most Zooplankton LW measurements were collected by GmbH in 2021; Cladoceran values came from literature reviews

2. Conversion factors from Waterborne:
  - These were determined from previous meetings and are for converting individuals/sample to individuals/area for the Mesocosm control data
  
3. Mesocosm effects data from Waterborne
  -abund_sum_lifestage = sample abundances, with lifestages rolled up into 1 value (e.g. can include larvae, pupae, adults)

```{r data}
# Compiled values for individual weights:
dw <- read.xlsx("Input/Zooplankton_Biomass_Conversions.xlsx", sheet = "zooplankton_weights")

# Conversion information:
cf <- read.xlsx("R_Analyses/SpeciesList_ControlData_v_Aquatox.xlsx",
                  sheet = "Species List for Conversions") %>%
  janitor::clean_names() %>%
  filter(parameter_group == "Zooplankton",
         #, consensus_group != "Nauplia" #remove nauplia filter fo effect size
         ) %>%
  dplyr::select(parameter_group:mesocosm_units, units_for_aquatox, apply_species_lw_data) %>%
      # Add the individual weight values, convert any in ug to mg:
  mutate(weight_per_ind = dw$weight_per_individual[match(.$apply_species_lw_data, dw$Taxon)],
         original_wt_units = dw$units_weight[match(.$apply_species_lw_data, dw$Taxon)],
         weight_mg_per_ind = ifelse(original_wt_units == "ug", weight_per_ind/1000, weight_per_ind)) # convert all weights to mg

cf$variable[cf$variable=="Diaptomidae (adult)"] <- "Diaptomidae" # rename to match control data merging later on
cf$variable[cf$variable=="Diaptomidae (Copepodit)"] <- "Diaptomidae" # rename to match control data merging later on
cf$variable[cf$variable=="Cyclopidae (adult)"] <- "Cyclopidae" # rename to match control data merging later on
cf$variable[cf$variable=="Cyclopidae (Copepodit)"] <- "Cyclopidae" # rename to match control data merging later on



# Control data
d.meso <- readRDS("Output/02_Effects_and_Calib_byGroup/sum_life_stages_bySpecies.rds") %>% 
  filter(parameter_group=="Zooplankton"
         #, variable != "Nauplia")# remove Nauplia filter for effect size calcs
        ) %>% 
  dplyr::select(study:treatment, abund_sum_lifestage)



# Combine control data w/conversion information:
d <- left_join(d.meso, cf, by = c("parameter_group", "consensus_group", "variable"))
# View(d %>% distinct(consensus_group, variable, weight_mg_per_ind)) # check, correct!
```

# Biomass Conversions
1. Calculate species-specific biomass
    * Vol_to_area ratio have been defined for cases when units change from volume to area (L to m2)
        * 1760 = volume of water (L) in the enclosures (i.e. total volume critters could live in)
        * 8.15 = area of enclosures (m2)
        
2. Sum biomass values by study, enclosure, date, and Aquatox record grouping (same as consensus_group)
    * We need to report 1 biomass value per study/enclosure/date/group.
    * Groupings are the same as consensus groups (i.e. one Aquatox record per consensus group)
```{r biomass_conversions}
#View(d %>% distinct(consensus_group, variable, units_or_id, units_for_aquatox))

#two scenarios: 
    # ind/L --> g/m2
    # ind/L --> mg/L

vol_to_area <- 1760/8.15

d.bio <- d %>%
  mutate(sp_biomass = case_when(
            units_or_id == "[Individuals/L]"  & units_for_aquatox == "mg/L dry" ~ abund_sum_lifestage*weight_mg_per_ind,
            units_or_id == "[Individuals/L]" & units_for_aquatox == "g/m2 dry" ~ (abund_sum_lifestage*vol_to_area*weight_mg_per_ind)/1000)) %>% # divide by 1000 to go from mg to g
  group_by(study, enclosure, date, consensus_group) %>%
  mutate(group_abundance = sum(abund_sum_lifestage),
         group_biomass = sum(sp_biomass)) %>% #STOP HERE for indv_biomass file
  distinct(study, enclosure, treatment, day, parameter_group, consensus_group, date, units_for_aquatox, group_biomass, group_abundance)

write.csv(d.bio, paste0("Output/07_Biomass_Conversions/Zooplankton_Biomass_by_ModeledGroups_", Sys.Date(), ".csv"))

write.csv(d.bio, paste0("Output/07_Biomass_Conversions/Zooplankton_Indv_Biomass_conversion.csv"))


```

```{r save_cf}
# Added 2/4 - saving conversion factor information for converting calibration criteria to biomass

cf.save <- cf %>%
  mutate(vol_to_area = ifelse(mesocosm_units == "[Individuals/L]" & units_for_aquatox == "g/m2 dry", vol_to_area, NA_real_))

write_csv(cf.save, "Output/07_Biomass_Conversions/Zooplankton_conv_factors.csv")
```



Subset table for Aquatox Overlay data file:

```{r A_overlay}

# Output in format for AQUATOX observed values overlay:
AQ_Zooplankton <- d.bio %>%
  dplyr::select(consensus_group, date, group_biomass, study, enclosure, treatment, day, units_for_aquatox, group_abundance) %>%
  rename(species_group = consensus_group) %>%
  mutate(non_detects = 0, 
         min_bar_value = group_biomass,
         max_bar_value = group_biomass)
write.csv(AQ_Zooplankton, paste0("Output/07_Biomass_Conversions/Aquatox_Zooplankton_Overlay_", Sys.Date(), ".csv"))

```

