---
title: "Effects Calibration Results & Reporting"
author: "A. Lindborg & L.Mudge"
date: "6/17/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---
# Purpose
Original purpose was to provide Waterborne with example plots of how we think the data should be visualized to compare control vs effects data and percent differences in model results compared to the MDD. 

Waterborne elected to use example plots from Isabel O'Conner. The script has been modified to create those plots.

From Waterborne: 
- Set of two plots
- The first plot should show both the measured and simulated abundances in control and treatment
- The second plot should show both the measured and simulated effect sizes and the MDD. 

**See Output/12_Percent_MDD_Plots folder folder for example plots from Isabel - Waterborne chose these as the plots they want to replicate 


# History
06/15/2022 - Create initial plots     A. Lindborg
07/18/2022 - Update plots to reflect request from Waterborne (above)    A. Lindborg
08/15/2022 - Fix plotting errors (aestetics) for both average & MDD plots  -L.Mudge
08/24/2022 - QA & rerunning with most recent results from D.Dawson - L.Mudge
08/26/2022 - Script adapted to include calculation of mean error & reporting for Waterborne Tables. -LMudge
08/31/2022 - Script modified to include results for no-effects species - L.Mudge
09/01/2022 - Updated with final run of highest treatment level simulation results (effects sp only). -L.Mudge
09/07/2022 - Updating to include assessment and plots of "no effects" species and lower treatment levels -L.MUDGE
09/22/2022 - Added Macrophytes. -L.Mudge
10/06/2022 - Update and rerun with final calibration model (FinalMod2_100201) - L.Mudge
11/28/2022-  Create a 'theme_big' to apply larger text size for abstract figures - L.Mudge

# Setup
```{r setup}
library(tidyverse)
library(readxl)
library(lubridate)
library(openxlsx)
library(ggpubr)
library(here)

theme <- theme(text = element_text(family = "sans")) +
  theme_bw() +
  theme(legend.title = element_blank(), legend.text = element_text(color="black", size=8),
        legend.background = element_rect( size=.5, linetype= "solid", color = "black")) +
  theme(panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black", size= 1)) +
  theme(axis.text.x = element_text(color="black", size=8, vjust=0.5, angle=0)) +
  theme(axis.text.y = element_text(color="black", size=8, vjust=0.5, angle=0)) +
  theme(axis.title.x = element_text(color="black", size=9, face="bold")) +
  theme(axis.title.y = element_text(color="black", size=9, face="bold")) +
  theme(plot.title = element_text(size = 10, hjust = 0.5, face="bold")) +
  theme(axis.ticks = element_line(size = 1)) +
  theme(axis.line = element_line(size = 1)) +
  theme(strip.background =element_rect(fill="white")) +
  theme(panel.border = element_rect(fill = NA, size = 0.25)) +
  theme(strip.text = element_text(face="bold", size = 9)) +
  theme(plot.margin = unit(c(0.5,0.5,.5,0.5), "cm"))


theme_big <- theme(text = element_text(family = "sans")) +
  theme_bw() +
  theme(legend.title = element_blank(), legend.text = element_text(color="black", size=12),
        legend.background = element_rect( size=.5, linetype= "solid", color = "black")) +
  theme(panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black", size= 1)) +
  theme(axis.text.x = element_text(color="black", size=12, vjust=0.5, angle=0)) +
  theme(axis.text.y = element_text(color="black", size=12, vjust=0.5, angle=0)) +
  theme(axis.title.x = element_text(color="black", size=13, face="bold")) +
  theme(axis.title.y = element_text(color="black", size=13, face="bold")) +
  theme(plot.title = element_text(size = 14, hjust = 0.5, face="bold")) +
  theme(axis.ticks = element_line(size = 1)) +
  theme(axis.line = element_line(size = 1)) +
  theme(strip.background =element_rect(fill="white")) +
  theme(panel.border = element_rect(fill = NA, size = 0.25)) +
  theme(strip.text = element_text(face="bold", size = 13)) +
  theme(plot.margin = unit(c(0.5,0.5,.5,0.5), "cm"))


options(scipen = 9999)

results_folder <- here("01_Aquatox_Results_Calibration_Effects", "FinalMod2_100201")
```

# Data
* Sample dates, MDD, and calibration criteria all from Waterborne, used for filtering data
```{r import_clean_data}
# sampling dates:
sd <- read.xlsx("\\\\integral-corp.com/data/C2000-C3999/C3143_Mesocosm_Waterborne/Data/Effect Criteria/AZT-effect-criteria-tables-Example_Jun2022.xlsx", 
                sheet = "SampleDates_LM", colNames=FALSE, detectDates= TRUE) %>% 
  pivot_longer(cols = X2:X15, names_to = "blank", values_to="date") %>%
  rename(parameter_group = X1) %>%
  dplyr::select(-blank) %>%
  group_by(parameter_group)

## Load criteria data for filtering perturbed data & adding reference info (parameter & consensus groups)
crit <- read_csv(here("01_Aquatox_Results_Calibration_Effects", "Input", "Calibration_Criteria_in_Biomass.csv"))  %>%
  mutate(aq_record = ifelse(is.na(aq_record), consensus_group, aq_record)) %>% # No AQ records for total perio or total phyto- so fill in
  add_row(parameter_group = "Macroinvertebrates", consensus_group = "Odonata", aq_record = "Total Odonata", units_for_aquatox = "g/m2 dry",
          crit_biomass_min = .$crit_biomass_min[.$aq_record == "Dragonfly_Meso (g/m2 dry)"], 
          crit_biomass_max = .$crit_biomass_max[.$aq_record == "Dragonfly_Meso (g/m2 dry)"],
          .after = 10)



## add mdd data
mdd <- read_xlsx("\\\\integral-corp.com/data/C2000-C3999/C3143_Mesocosm_Waterborne/Data/Effect Criteria/MDD/MDD_Input.xlsx", sheet = 2)
mdd$date <- as.Date(mdd$date, format = "%m/%d/%Y") #fix date

## List of species with observed effects in Mesocosm studies: these are the Aquatox Record names, to use for filtering:
critters <- c("Phyto Diatom_Meso (mg/L dry)",
              "Phyto Crypto_Meso (mg/L dry)", 
              "Cyclopidae_Meso (mg/L dry)", 
              "Keratella_Meso (mg/L dry)",
              "CladoceranSmall_Meso (mg/L dry)",
              "Daphnidae_Meso (mg/L dry)")

## Observed effects -- all species & all treament levels
all.obs.eff <- read_csv(here("Output", "14_Observed_Effect_Size_Tables", "Observed_Effect_Sizes_all_treatments_and_groups.csv"))

```


```{r simulated_effects_data}
files <- list.files(path = results_folder,
                    pattern = "*.xls",
                    full.names = TRUE)

set_col_types <- c("date", "date", rep("numeric", times=49))

### Format AQ model results
aq.results <- tibble(filename = files) %>%
  mutate(contents = map(filename, ~readxl::read_excel(.x, col_types = set_col_types))) %>%
  unnest(cols=contents) %>%
  dplyr::select(1:2, 19:47) %>% #Keep filename, date, and organism cols only
  rename(date = `Date:`) %>%
  extract(col = filename, into=c("filename", "treatment"), "(.*)_([^_]+).xls") %>%
  mutate(
    treatment = case_when(
      treatment == "03ugL" ~ "0.3 ug/L",
      treatment == "10ugL" ~ "10 ug/L",
      treatment == "1ugL" ~ "1 ug/L",
      treatment == "33ugL" ~ "33 ug/L",
      treatment == "3ugL" ~ "3 ug/L",
      treatment == "C" ~ "Control")) %>%
  dplyr::select(-filename) %>%
  pivot_longer(cols= -c(date, treatment),
               names_to = "aq_record",
               values_to = "model_result") %>%
  mutate(year = lubridate::year(date)) %>%
  mutate(date.obj = as.Date(date)) %>%
  #filter(aq_record %in% unique(crit$aq_record)) %>%
  #filter(date.obj >= exp.dates$min_date[match(year, exp.dates$year)] & date.obj <= exp.dates$max_date[match(year, exp.dates$year)]) %>%
  arrange(aq_record) %>%
  left_join(., crit%>%dplyr::select(parameter_group, consensus_group, aq_record)) %>%
  mutate(parameter_group = replace_na(parameter_group, "Macrophytes"),
         consensus_group = replace_na(consensus_group, "Macrophytes"))

#write_csv(aq.results, "compiled_aquatox_results.csv")

```

```{r sim_data_old, include= FALSE}
### SIMULATED MODEL RESULTS ###



   # CONROL #
aq.results.control <- read_csv(here("01_Aquatox_Results_Calibration_Effects", "Input", "aq_control_results_all.csv")) %>%
  filter(year %in% c("2019")) %>%
  rename(control = model_result) %>%
  left_join(., crit%>%dplyr::select(parameter_group, consensus_group, aq_record))
aq.results.control$Date <- as.Date(aq.results.control$Date, format = "%m/%d/%Y") #fix date






  # TREATMENT/PERTURBED #
aq.results.perturbed <- read_csv(paste0(results_folder, "/Calibration_Uncertainty_UMv7_BGToxMods_5200112.CSV")) %>%
  dplyr::select(c(1, 18:46)) ##CHECK WITH EACH DATA FILE UPLOADED THAT WE ARE KEEPING ALL CRITTERS

aq.results.perturbed$Date <- as.Date(aq.results.perturbed$Date, format = "%m/%d/%Y") #fix date

aq.results.pert <- aq.results.perturbed %>%
  #dplyr::select(-c(`...2`)) %>% #remove unnecessary columns
  #rename(Date = `Date:`) %>% #rename Date: column
  pivot_longer(cols= -c(Date), #Pivot data to long format
                names_to = "aq_record",
                values_to = "model_result") %>%
  mutate(year = lubridate::year(Date)) %>% #create year column
  mutate(date.obj = as.Date(Date)) %>% #create data object column
  left_join(., crit%>%dplyr::select(parameter_group, consensus_group, aq_record)) %>%
  filter(aq_record %in% unique(crit$aq_record)) %>% #filter for only those groups that have a criteria value
    arrange(aq_record)

aq.results.pert.final <- aq.results.pert %>%
    rename(perturbed = model_result)



```

* Mesocosm / Measured Biomass Data
```{r macrophytes_added_09222022}

### MEASURED MESOCOSM DATA - Macrophytes only, added after initial run ###

macrophytes <- readRDS("\\\\integral-corp.com/data/C2000-C3999/C3143_Mesocosm_Waterborne/Working_Files/R_Analyses/02_Model_Calibration_Effects/Output/02_Effects_and_Calib_byGroup/sum_life_stages_bySpecies.rds") %>% 
  filter(parameter_group == "Macrophytes") %>%
  filter(variable == "Myriophyllum spicatum" | variable == "Chara globularis") %>% 
  rename(species_group = variable,
         biomass = abund_sum_lifestage) %>%
  dplyr::select(-c(peak_date_start:criteria_midpoint), -date2, -units_or_id) %>%
  mutate(units_for_aquatox = "g/m2 dry",
         consensus_group = "Macrophytes",
         aq_record = case_when(
           species_group == "Chara globularis" ~ "Chara_Meso (g/m2 dry)",
           species_group == "Myriophyllum spicatum" ~ "Myriophyllum_Meso (g/m2 dry)"),
         year=2019)


macro.obs <- macrophytes %>%
  mutate(treatment = paste0("treatment_", treatment)) %>%
  group_by(treatment, aq_record, date) %>%
  mutate(mean = mean(biomass),
            min = min(biomass),
            max = max(biomass)) %>%
  distinct(aq_record, date, .keep_all = TRUE) %>%
  select(treatment, day, parameter_group, date, consensus_group, aq_record, mean) %>%
  pivot_wider(names_from = treatment, values_from = mean) %>%
  mutate(across(.cols=treatment_1:treatment_6, ~((.x-treatment_1)/treatment_1)*100))

```

```{r measured_data}

### MEASURED MESOCOSM DATA ###


## Load measured control and effects data and summarize to obtain one measurement for every unique treatment, critter and date to match how Waterborne plotted their data and calculated their effect sizes

d.measured <- read_csv(here("01_Aquatox_Results_Calibration_Effects", "Input", "mesocosm_treatment_data.csv")) %>%
  bind_rows(., macrophytes) %>%
  group_by(treatment, aq_record, date) %>%
  #mutate(biomass = mean(biomass))
  mutate(mean = mean(biomass),
            min = min(biomass),
            max = max(biomass)) %>%
  dplyr::select(-enclosure, -biomass) %>% # remove vars only needed for individual enclosure measurements - lm 8/26
  distinct(aq_record, date, .keep_all = TRUE) %>%
  ungroup() %>%
  mutate(date = as.Date(date))


# Create long version of effects sizes
all.obs.eff.long <- all.obs.eff %>%
  bind_rows(., macro.obs) %>%
  pivot_longer(cols = treatment_1:treatment_6, names_to = "treatment", values_to = "observed_effect") %>%
  mutate(treatment = as.numeric(str_extract_all(treatment, "[0-9]+")),
         observed_effect = round(observed_effect, 2))

# Join measured data and long version of effects data
d.measured.wEffects <- left_join(d.measured, all.obs.eff.long)

```

# Calculate Effect Size of Simulation
Equations from Waterborne, see word doc: AZT_effect_criteria_June_2022.docx

%effect_sim= (Treatment - Control) * 100 / Control

```{r calc_sim_effect_size}


  # COMBINED ALL SIMULATED RESULTS & CALCULATE SIMULATED EFFECT SIZE #
# aq.all <- inner_join(aq.results.control, aq.results.pert.final, by = c("Date", "aq_record", "year", "date.obj", "parameter_group", "consensus_group")) %>% rename(date = Date) %>%
#     mutate(simulated_effect=((perturbed-control)/control)*100) #QA - switched numerator to match Waterborne equation  LM

# UPDATED 9/2 WITH RESULTS FOR ALL TREATMENT LEVELS
aq.all <- aq.results %>%
  pivot_wider(names_from =treatment, values_from = model_result)
aq.all <- aq.all %>%
  mutate(across(.cols = c(`0.3 ug/L`:`3 ug/L`), 
                .fns = list(effect_size = ~((.x-Control)/Control)*100), 
                .names="{.col}_{.fn}"))



treatment_key <- data.frame(
  treat.num = c(1,2,3,4,5,6),
  treat.name = c("Control", "0.3 ug/L", "1 ug/L", "3 ug/L", "10 ug/L", "33 ug/L" )
)

# Get just the effect sizes for each of the treatment levels -- use this for plotting
eff_size <- aq.all %>%
  dplyr::select(-c(`0.3 ug/L`:Control)) %>%
  pivot_longer(cols = c(`0.3 ug/L_effect_size`:`3 ug/L_effect_size`), names_to = "treat.name", values_to = "simulated_effect") %>%
  mutate(treat.name = str_remove_all(treat.name, "\\_effect\\_size")) %>%
  #filter(!treat.name %in% "33 ug/L") %>%
  left_join(., treatment_key) %>%
  rename(treatment = treat.num)
  
  
```



# EVALUATION OF SPEICES WITH TREATMENT RELATED EFFECTS
* This section produces the plots & tabular results (sim effect size, mean error) requested by Waterborne

## TABLES
* Creates unformatted criteria tables with sample dates, MDD, observed and simulated effect sizes, and ME. Setup in away to copy/paste the simualted effect & ME directly into the Excel workbook for waterborne AND use the day/MDD/obs effect sizes as a QA check when compared to the values already filled in by Waterborne.

*Calculate Mean Error: ME=|%effect_sim-%effect_obs|
```{r report_tables}
tab <- mdd %>%
  left_join(., aq.all) %>%
    dplyr::select(c(date, aq_record, day, MDD_max, observed_effect, parameter_group, consensus_group, `33 ug/L_effect_size`)) %>%
  rename(simulated_effect= `33 ug/L_effect_size`) %>%
  # Calc Mean Error
  mutate(mean_error = abs(simulated_effect-observed_effect)) %>%
  # Reformat
  #dplyr::select(c(date, aq_record, day, MDD_max, observed_effect, parameter_group, consensus_group, simulated_effect, mean_error)) %>%
  arrange(date) %>%
  pivot_longer(cols = c(day, MDD_max, observed_effect, simulated_effect, mean_error), names_to = "variable") %>%
  mutate(value=signif(value, 3)) %>%
  nest(data=c(consensus_group, aq_record,date, variable, value)) %>%
  mutate(data = map(data, ~.x %>% pivot_wider(names_from = "date"))) %>%
  pwalk(~write_csv(x=.y, file = paste0("01_Aquatox_Results_Calibration_Effects/Output/Integral_CriteriaTables_",.x, "_", Sys.Date(), ".csv"))) #creates 1 csv per nested df

  


```


## PLOTS 
Final plots per Waterborne specifications above. 
*switch +theme or +theme_big depending on what text size you want printed.
```{r report_plots_final}

# Combine the observed and simulated effects for plotting:
p.effects <- d.measured.wEffects %>%
  distinct(date, aq_record, treatment, observed_effect) %>% # get sampling dates we are comparing too
  filter(aq_record %in% critters, treatment %in% c(2:6)) %>% # filter to end up with only no-effect species for all treatments 
  left_join(., eff_size) %>% #
  filter(treatment==6) %>%
  dplyr::select(treatment, date, aq_record, observed_effect, parameter_group, consensus_group, simulated_effect) %>%
  pivot_longer(cols = c(observed_effect, simulated_effect), names_to = "effect_type", values_to="effect_size") %>%
  mutate(date = as.Date(date))

min_date <- as.Date("2019-06-01")
max_date <- as.Date("2019-09-06")

pdf(paste0(here("01_Aquatox_Results_Calibration_Effects", "Output", "Integral_Sp_Effects_Plots_"), Sys.Date(), ".pdf", sep=""), paper="USr", width=10, height=7.25)
par(omi=c(1.5,0.5,0,0.5), pin=c(7,8),pty='m')

for(i in unique(p.effects$parameter_group)){
  pd <- p.effects %>% filter(parameter_group == i) %>% arrange(consensus_group, aq_record)
  
  for(j in unique(pd$aq_record)){
  
  #get aquatox data
    #ad <- pd %>% filter(aq_record == j)
  ad <- aq.all %>% filter(aq_record == j)   ## has col for control + one for each trt level
  
  # get measured data
  mt <- d.measured %>% filter(aq_record ==j, treatment==6)
  mc <- d.measured %>% filter(aq_record ==j, treatment ==1)
  
  #get mdd data
  md <- mdd %>% filter(aq_record == j)
  
  #ed <- d.effects.treatment6 %>% filter(aq_record == j)
  ed <- p.effects %>% filter(aq_record ==j)
  
  #add control data
  #cd <- d.control %>% filter(aq_record == j)
  
  units <- regmatches(j, gregexpr("(?=\\().*?(?<=\\))", j, perl=T))[[1]]
  
  #AVERAGE PLOTS (same as script #11)
  p1 <- ggplot() +
    # Treatment:
    geom_point(data = mt, aes(x = date, y = mean, colour = "red")) +
    geom_linerange(data = mt, aes(x = date, ymin = min, ymax= max, xmin = min_date, xmax = max_date), colour = "red") + #measured treatment
    geom_path(data = ad, aes(x = date.obj, y = `33 ug/L`, colour = "red", linetype = "Simulated treatment")) + #simulated treatment
    
    # Control:
    geom_point(data = mc, aes(x = date, y = mean, colour = "green4")) +
    geom_linerange(data = mc, aes(x = date, ymin = min, ymax= max, xmin = min_date, xmax = max_date), colour = "green4") + #measured control
    geom_path(data = ad, aes(x = date.obj, y = Control, colour = "green4", linetype = "Simulated control")) + #simulated control
  
    # POINTS legend:   #keep this order to match lines
    scale_color_identity(breaks = c( "green4", "red"), labels = c( "Measured Control", "Measured Treatment"), guide = "legend") + 
  
    # LINES legend:   #Green=Sim control; red= Sim treatment
    scale_linetype_manual(values = c(1,1), guide = guide_legend(override.aes = list(color= c("green4", "red")))) + 
  
    # Axes/Labels
    scale_x_date(limits=c(min_date, max_date), date_breaks = "5 days", date_labels = "%b-%d") +
    labs(x= "", 
         y= paste0("Biomass ", units), 
        title = paste0("Parameter Group: ", i, "\nConsensus Group: ", unique(ed$consensus_group), "\nAQUATOX record: ", j, "\nTreatment: Highest Dose (33 ug/l)")) +
    theme +
    theme(legend.title = element_blank(),
          axis.text.x = element_text(angle = 45, vjust = 1.3, hjust = 1.3))
  


  p2 <- ggplot() +
     geom_point(data = ad, aes(x=date.obj, y = `33 ug/L_effect_size`, color= "Simulated Effect")) + 
     geom_point(data = md, aes(x = date, y = observed_effect, colour = effect_outcome)) + #Two outcomes = Effect or No
     geom_ribbon(data = md, aes(x= date, ymin = MDD_min, ymax = MDD_max, fill = "grey65"),  alpha = 0.2) +
     
     #POINTS legend: Ggplot assigns color based on alpha order of aes variable= Effect, No Effect, Simulated Effect
     scale_colour_manual(values = c("red", "black", "lightblue3"),  
                      labels = c("Measured With Effect", "Measured Without Effect", "Simulated Effect Size")) + 
     
     #FILL legend
     scale_fill_manual("", label = "%MDD",values="grey65") +
     
     #Axes/Labels
     scale_x_date(limits=c(min_date, max_date), date_breaks = "5 days", date_labels = "%b-%d") +
     labs(x= "", y= paste0("Percent"), 
          title = paste0("Parameter Group: ", i, "\nConsensus Group: ", unique(ad$consensus_group), "\nAQUATOX record: ", j)) +
     theme +
     theme(plot.title = element_blank(),
           legend.title = element_blank(),
           axis.text.x = element_text(angle = 45, vjust = 1.3, hjust = 1.3))
  
  print(ggarrange(p1, p2,
          ncol = 1, nrow = 2))
  }
}


dev.off()
```

```{r plots_SETAC_abstract_Fig2}

# Combine the observed and simulated effects for plotting:
abs_grps <- c("Copepoda_predatory", "Daphnidae", "Rotifera_herbivorous2")

d.abs <- p.effects %>% 
  filter(consensus_group %in% abs_grps) %>%
  mutate(consensus_groupF =factor(consensus_group, levels=c("Copepoda_predatory", "Daphnidae", "Rotifera_herbivorous2"), ordered=TRUE))

min_date <- as.Date("2019-06-01")
max_date <- as.Date("2019-09-06")

pdf(paste0(here("01_Aquatox_Results_Calibration_Effects", "Output", "SETAC_Fig2"), Sys.Date(), ".pdf", sep=""), paper="USr", width=10, height=7.25)
par(omi=c(1.5,0.5,0,0.5), pin=c(7,8),pty='m')

for(i in unique(d.abs$parameter_group)){
  pd <- d.abs %>% filter(parameter_group == i) %>% arrange(consensus_group, aq_record)
  
  for(j in unique(pd$aq_record)){
  
  #get aquatox data
    #ad <- pd %>% filter(aq_record == j)
  ad <- aq.all %>% filter(aq_record == j)   ## has col for control + one for each trt level
  
  # get measured data
  mt <- d.measured %>% filter(aq_record ==j, treatment==6)
  mc <- d.measured %>% filter(aq_record ==j, treatment ==1)
  
  #get mdd data
  md <- mdd %>% filter(aq_record == j)
  
  #ed <- d.effects.treatment6 %>% filter(aq_record == j)
  ed <- d.abs %>% filter(aq_record ==j)
  
  #add control data
  #cd <- d.control %>% filter(aq_record == j)
  
  units <- regmatches(j, gregexpr("(?=\\().*?(?<=\\))", j, perl=T))[[1]]
  
  #AVERAGE PLOTS (same as script #11)
  p1 <- ggplot() +
    # Treatment:
    geom_point(data = mt, aes(x = date, y = mean, colour = "red")) +
    geom_linerange(data = mt, aes(x = date, ymin = min, ymax= max, xmin = min_date, xmax = max_date), colour = "red") + #measured treatment
    geom_path(data = ad, aes(x = date.obj, y = `33 ug/L`, colour = "red", linetype = "Simulated treatment")) + #simulated treatment
    
    # Control:
    geom_point(data = mc, aes(x = date, y = mean, colour = "green4")) +
    geom_linerange(data = mc, aes(x = date, ymin = min, ymax= max, xmin = min_date, xmax = max_date), colour = "green4") + #measured control
    geom_path(data = ad, aes(x = date.obj, y = Control, colour = "green4", linetype = "Simulated control")) + #simulated control
  
    # POINTS legend:   #keep this order to match lines
    scale_color_identity(breaks = c( "green4", "red"), labels = c( "Measured Control", "Measured Treatment"), guide = "legend") + 
  
    # LINES legend:   #Green=Sim control; red= Sim treatment
    scale_linetype_manual(values = c(1,1), guide = guide_legend(override.aes = list(color= c("green4", "red")))) + 
  
    # Axes/Labels
    scale_x_date(limits=c(min_date, max_date), date_breaks = "5 days", date_labels = "%b-%d") +
    labs(x= "", 
         y= paste0("Biomass ", units), 
        title = paste0("Consensus Group: ", unique(ed$consensus_group), "\n ")) +
    theme_big +
    theme(legend.title = element_blank(),
          axis.text.x = element_text(angle = 45, vjust = 1.3, hjust = 1.3))
  

  print(p1)
  }
}


dev.off()

```


```{r report_plots_original}

##create subsets for treatment groups and species 
d.effects.treatment6 <- d.measured %>%
  filter(treatment == 6) %>%
  mutate(treatment = case_when(
    treatment == "6" ~ "Highest Dose (33 ug/L)")) %>%
  filter(aq_record %in% critters)

d.control <- d.measured %>%
  filter(treatment == 1) %>%
  mutate(treatment = case_when(
      treatment == "1" ~ "Control")) %>%
  filter(aq_record %in% critters)

aq.filt <- aq.all %>%
  filter(aq_record %in% critters) #%>%
  #rename(date = date.obj)

# Set min and max dates for X-axis, as requested by B.Sackmann:
min_date <- as.Date("2019-06-01")
max_date <- as.Date("2019-09-06")

pdf(paste0("01_Aquatox_Results_Calibration_Effects/Output/Integral_Sp_Effects_Plots_", Sys.Date(), ".pdf", sep=""), paper="USr", width=10, height=7.25)
par(omi=c(1.5,0.5,0,0.5), pin=c(7,8),pty='m')

for(i in unique(aq.filt$parameter_group)){
  pd <- aq.filt %>% filter(parameter_group == i) %>% arrange(consensus_group, aq_record)
  
  for(j in unique(pd$aq_record)){
  
  #add aquatox data
  ad <- pd %>% filter(aq_record == j)
  
  #add mdd data
  md <- mdd %>% filter(aq_record == j)
  
   ed <- d.effects.treatment6 %>% filter(aq_record == j)
  
  #add control data
  cd <- d.control %>% filter(aq_record == j)
  
  units <- regmatches(j, gregexpr("(?=\\().*?(?<=\\))", j, perl=T))[[1]]
  
  #AVERAGE PLOTS (same as script #11)
  p1 <- ggplot() +
    # Treatment:
    geom_point(data = ed, aes(x = date, y = mean, colour = "red")) +
    geom_linerange(data = ed, aes(x = date, ymin = min, ymax= max, xmin = min_date, xmax = max_date), colour = "red") + #measured treatment
    geom_path(data = ad, aes(x = date, y = perturbed, colour = "red", linetype = "Simulated treatment")) + #simulated treatment
    
    # Control:
    geom_point(data = cd, aes(x = date, y = mean, colour = "green4")) +
    geom_linerange(data = cd, aes(x = date, ymin = min, ymax= max, xmin = min_date, xmax = max_date), colour = "green4") + #measured control
    geom_path(data = ad, aes(x = date, y = control, colour = "green4", linetype = "Simulated control")) + #simulated control
  
    # POINTS legend:   #keep this order to match lines
    scale_color_identity(breaks = c( "green4", "red"), labels = c( "Measured Control", "Measured Treatment"), guide = "legend") + 
  
    # LINES legend:   #Green=Sim control; red= Sim treatment
    scale_linetype_manual(values = c(1,1), guide = guide_legend(override.aes = list(color= c("green4", "red")))) + 
  
    # Axes/Labels
    scale_x_date(limits=c(min_date, max_date), date_breaks = "5 days", date_labels = "%b-%d") +
    labs(x= "", 
         y= paste0("Biomass ", units), 
        title = paste0("Parameter Group: ", i, "\nConsensus Group: ", unique(ed$consensus_group), "\nAQUATOX record: ", j)) +
    theme +
    theme(legend.title = element_blank(),
          axis.text.x = element_text(angle = 45, vjust = 1.3, hjust = 1.3))
  
  
  
   #MDD PLOTS
   p2 <- ggplot() +
     geom_point(data = ad, aes(x=date, y = simulated_effect, colour = "Simulated Effect")) + 
     geom_point(data = md, aes(x = date, y = observed_effect, colour = effect_outcome)) + #Two outcomes = Effect or No
     geom_ribbon(data = md, aes(x= date, ymin = MDD_min, ymax = MDD_max, fill = "grey65"),  alpha = 0.2) +
     
     #POINTS legend: Ggplot assigns color based on alpha order of aes variable= Effect, No Effect, Simulated Effect
     scale_colour_manual(values = c("red", "black", "lightblue3"),  
                      labels = c("Measured With Effect", "Measured Without Effect", "Simulated Effect Size")) + 
     
     #FILL legend
     scale_fill_manual("", label = "%MDD",values="grey65") +
     
     #Axes/Labels
     scale_x_date(limits=c(min_date, max_date), date_breaks = "5 days", date_labels = "%b-%d") +
     labs(x= "", y= paste0("Percent"), 
          title = paste0("Parameter Group: ", i, "\nConsensus Group: ", unique(ad$consensus_group), "\nAQUATOX record: ", j)) +
     theme +
     theme(plot.title = element_blank(),
           legend.title = element_blank(),
           axis.text.x = element_text(angle = 45, vjust = 1.3, hjust = 1.3))
   
print(ggarrange(p1, p2,
          ncol = 1, nrow = 2))
 
  }
}

dev.off()


# FOR PLOT TESTING:
#i <- "Zooplankton"
#j <- "CladoceranSmall_Meso (mg/L dry)"
#ggplotly(p1) # use plotly to verify that what is labeled as simulated/measured and control/treatment actually match the data!
#ggplotply(p2)

```



# EVALUATION OF SPECIES WITHOUT TREATMENT RELATED EFFECTS 
* Simulations need to be evaluated for relative effect sizes across all treatment levels

## Were simulated effects <20% & what is the occurrence of >= 20% simulated effects?
* IF model results show effects >=20% for more than 1 sampling data, need to discuss

```{r no_effects_sp_occurrence}

# Q: Were simulated effects < 20%?
no_eff <- d.measured.wEffects %>%
  distinct(date, aq_record, treatment, observed_effect) %>% # get sampling dates we are comparing too
  filter(!grepl("Total", aq_record), !is.na(aq_record), !aq_record %in% critters, treatment %in% c(2:6)) %>% # filter to end up with only no-effect species for all treatments 
  left_join(., eff_size) %>% #join aq data to measured, that way will only keep the experiment sampling dates
  mutate(effect_less20 = ifelse(abs(simulated_effect)<20, TRUE, FALSE))

# Calculate occurrence of >=20% simulated effects:
effect_more20 <- no_eff %>%
  group_by(aq_record, treatment) %>%
  count(effect_less20)

to_explain <- effect_more20 %>%
  filter(effect_less20 ==FALSE & n >1) %>%
  left_join(., treatment_key%>%rename(treatment=treat.num))

write_csv(to_explain, here("01_Aquatox_Results_Calibration_Effects", "Output", "LowerTreatmentSpGreater20.csv"))
```

## NO EFFECTS PLOTS

1) For all "no-effects" species, need to plot observed and simulated effects over time for highest treatment level (33 ug/L). Where relative effect sizes are >=20% in simulation, effects should be identified in the plots


```{r plots_no_effect_sp_33ug}

p.noeff <- no_eff %>% 
  filter(treatment==6) %>%
  dplyr::select(treatment, date, aq_record, observed_effect, parameter_group, consensus_group, simulated_effect, effect_less20) %>%
  pivot_longer(cols = c(observed_effect, simulated_effect), names_to = "effect_type", values_to="effect_size") %>%
  mutate(date = as.Date(date))

min_date <- as.Date("2019-06-01")
max_date <- as.Date("2019-09-06")

pdf(paste0(here("01_Aquatox_Results_Calibration_Effects", "Output", "Integral_No_Effects_Sp_33ug"), Sys.Date(), ".pdf", sep=""), paper="USr", width=10, height=7.25)
par(omi=c(1.5,0.5,0,0.5), pin=c(7,8),pty='m')

for(i in unique(p.noeff$parameter_group)){
  pd <- p.noeff %>% filter(parameter_group == i) %>% arrange(consensus_group, aq_record)
  
  for(j in unique(pd$aq_record)){
  
  #add aquatox data
    #ad <- pd %>% filter(aq_record == j)
  ad <- aq.all %>% filter(aq_record == j)   ## has col for control + one for each trt level
  
  # measured data
  mt <- d.measured %>% filter(aq_record ==j, treatment==6)
  mc <- d.measured %>% filter(aq_record ==j, treatment ==1)
  #add mdd data
  #md <- mdd %>% filter(aq_record == j)
  
  #ed <- d.effects.treatment6 %>% filter(aq_record == j)
  ed <- p.noeff %>% filter(aq_record ==j)
  
  #add control data
  #cd <- d.control %>% filter(aq_record == j)
  
  units <- regmatches(j, gregexpr("(?=\\().*?(?<=\\))", j, perl=T))[[1]]
  
  #AVERAGE PLOTS (same as script #11)
  p1 <- ggplot() +
    # Treatment:
    geom_point(data = mt, aes(x = date, y = mean, colour = "red")) +
    geom_linerange(data = mt, aes(x = date, ymin = min, ymax= max, xmin = min_date, xmax = max_date), colour = "red") + #measured treatment
    geom_path(data = ad, aes(x = date.obj, y = `33 ug/L`, colour = "red", linetype = "Simulated treatment")) + #simulated treatment
    
    # Control:
    geom_point(data = mc, aes(x = date, y = mean, colour = "green4")) +
    geom_linerange(data = mc, aes(x = date, ymin = min, ymax= max, xmin = min_date, xmax = max_date), colour = "green4") + #measured control
    geom_path(data = ad, aes(x = date.obj, y = Control, colour = "green4", linetype = "Simulated control")) + #simulated control
  
    # POINTS legend:   #keep this order to match lines
    scale_color_identity(breaks = c( "green4", "red"), labels = c( "Measured Control", "Measured Treatment"), guide = "legend") + 
  
    # LINES legend:   #Green=Sim control; red= Sim treatment
    scale_linetype_manual(values = c(1,1), guide = guide_legend(override.aes = list(color= c("green4", "red")))) + 
  
    # Axes/Labels
    scale_x_date(limits=c(min_date, max_date), date_breaks = "5 days", date_labels = "%b-%d") +
    labs(x= "", 
         y= paste0("Biomass ", units), 
        title = paste0("Parameter Group: ", i, "\nConsensus Group: ", unique(ed$consensus_group), "\nAQUATOX record: ", j, "\nTreatment: Highest Dose (33 ug/l)")) +
    theme +
    theme(legend.title = element_blank(),
          axis.text.x = element_text(angle = 45, vjust = 1.3, hjust = 1.3))
  


  p2 <- ggplot(data=ed) +
    geom_point(aes(x=date, y=effect_size, color=effect_type)) + #, shape=effect_less20
    geom_ribbon(aes(x=date,ymin = -20, ymax = 20, fill= "grey65"),  alpha = 0.1) +
    scale_color_manual(values = c("green4", "red"), labels =c("Observed Effect", "Simulated Effect"), guide="legend") +
    #scale_shape_manual(name = "Effect <20%?", values=c(16,8), guide="legend", drop=FALSE) +
    labs(x="Date", 
         y= "Effect Size"#,
        #title = paste0("Parameter Group: ", unique(ed$parameter_group), "\nConsensus Group: ", unique(ed$consensus_group), "\nAQUATOX record: ", i, "\nTreatment: Highest Dose (33 ug/l)")
        ) +
    scale_x_date(limits=c(min_date, max_date), date_breaks = "5 days", date_labels = "%b-%d") +
    scale_fill_manual("", label = "20% Effect Size \nThreshold",values="grey65") +
    theme +
    theme(axis.text.x = element_text(angle=90))
  
  print(ggarrange(p1, p2,
          ncol = 1, nrow = 2))
  }
}
  


dev.off()


```

2) If relative effect sizes >=20% are simulated in lower treatment levels, provide plots of those effects (i.e. plots of species/trt level combos in "to_explain", other than highest trt level)
 * QA check: no observations/measured data for herbivorous copepods? Should we make all records NA? (one date at -100%)
 
 **VIP NOTE this code is imperfect: would need to modify if want to plot more than just the 10ug/l treatment level. Happened this way just because adding the top panel in at the last minute and would require some code reworking to facet by treatment level.Therefore, with any new results run, you need to CHECK the "to_explain" dataframe and see if there are any other treatment levels we need to visualize.-LM 9/22/2022**
 

```{r no_effects_lower_trt_level}

# Need to make sure only making plots for the treatment levels where we saw the >=20%
pd.exp <- to_explain %>% dplyr::select(aq_record, treatment) %>%
  inner_join(., no_eff) %>% 
  filter(!treatment %in% c(1,6)) %>% # Remove control & highest treatment level
  dplyr::select(treatment, date, aq_record, observed_effect, parameter_group, consensus_group, simulated_effect, effect_less20) %>%
  pivot_longer(cols = c(observed_effect, simulated_effect), names_to = "effect_type", values_to="effect_size") %>%
  left_join(., treatment_key %>% rename(treatment=treat.num)) %>%
  mutate(date = as.Date(date)) %>%
  mutate(effect_size = ifelse(aq_record == "Calanoida_Meso (mg/L dry)" & effect_type == "observed_effect", NA, effect_size)) %>%
  arrange(parameter_group, consensus_group, aq_record)



min_date <- as.Date("2019-06-01")
max_date <- as.Date("2019-09-06")

pdf(paste0(here("01_Aquatox_Results_Calibration_Effects", "Output", "Integral_No_Effects_Sp_lower_trt_levels"), Sys.Date(), ".pdf", sep=""), paper="USr", width=10, height=7.25)
par(omi=c(1.5,0.5,0,0.5), pin=c(7,8),pty='m')
for(j in unique(pd.exp$aq_record)){
  
    #add aquatox data
    #ad <- pd %>% filter(aq_record == j)
  ad <- aq.all %>% filter(aq_record == j)   ## has col for control + one for each trt level
  
  # measured data
  mt <- d.measured %>% filter(aq_record ==j, treatment ==5) #%>% mutate(treat.name == "10 ug/L") #Note: doing this for brevity, will not work in future if need to show other treatment levels
  mc <- d.measured %>% filter(aq_record ==j, treatment ==1)
  #add mdd data
  #md <- mdd %>% filter(aq_record == j)
  
  #ed <- d.effects.treatment6 %>% filter(aq_record == j)
  ed <- p.noeff %>% filter(aq_record ==j)

    units <- regmatches(j, gregexpr("(?=\\().*?(?<=\\))", j, perl=T))[[1]]
  
  #AVERAGE PLOTS (same as script #11)
  p1 <- ggplot() +
    # Treatment:
    geom_point(data = mt, aes(x = date, y = mean, colour = "red")) +
    geom_linerange(data = mt, aes(x = date, ymin = min, ymax= max, xmin = min_date, xmax = max_date), colour = "red") + #measured treatment
    geom_path(data = ad, aes(x = date.obj, y = `10 ug/L`, colour = "red", linetype = "Simulated treatment")) + #simulated treatment
    
    # Control:
    geom_point(data = mc, aes(x = date, y = mean, colour = "green4")) +
    geom_linerange(data = mc, aes(x = date, ymin = min, ymax= max, xmin = min_date, xmax = max_date), colour = "green4") + #measured control
    geom_path(data = ad, aes(x = date.obj, y = Control, colour = "green4", linetype = "Simulated control")) + #simulated control
  
    # POINTS legend:   #keep this order to match lines
    scale_color_identity(breaks = c( "green4", "red"), labels = c( "Measured Control", "Measured Treatment"), guide = "legend") + 
  
    # LINES legend:   #Green=Sim control; red= Sim treatment
    scale_linetype_manual(values = c(1,1), guide = guide_legend(override.aes = list(color= c("green4", "red")))) + 
  
    # Axes/Labels
    scale_x_date(limits=c(min_date, max_date), date_breaks = "5 days", date_labels = "%b-%d") +
    labs(x= "", 
         y= paste0("Biomass ", units), 
        title = paste0("Parameter Group: ", unique(ed$parameter_group), "\nConsensus Group: ", unique(ed$consensus_group), "\nAQUATOX record: ", j, "\nTreatment: ", unique(pd.exp$treat.name))) +
    theme +
    theme(legend.title = element_blank(),
          axis.text.x = element_text(angle = 45, vjust = 1.3, hjust = 1.3))
  
  
  
  d <- pd.exp %>% filter(aq_record == j)
  p2 <- ggplot(data=d) +
    geom_point(aes(x=date, y=effect_size, color=effect_type)) + #, shape=effect_less20
    geom_ribbon(aes(x=date,ymin = -20, ymax = 20, fill = "grey65"),  alpha = 0.1) +
    scale_color_manual(values = c("green4", "red"), labels =c("Observed Effect", "Simulated Effect"), guide="legend") +
    #scale_shape_manual(name = "Effect <20%?", values=c(16,8), guide="legend", drop=FALSE) +
    labs(x="Date", 
         y= "Effect Size"#,
       # title = paste0("Parameter Group: ", unique(d$parameter_group), "\nConsensus Group: ", unique(d$consensus_group), "\nAQUATOX record: ", j)
        ) +
    scale_x_date(limits=c(min_date, max_date), date_breaks = "5 days", date_labels = "%b-%d") +
    scale_fill_manual("", label = "20% Effect Size \nThreshold",values="grey65") +
    theme +
    theme(axis.text.x = element_text(angle=90)) +
    facet_wrap(~treat.name)
    
  print(ggarrange(p1, p2,
          ncol = 1, nrow = 2))
      

}
dev.off()


  
```

