---
title: "Make intermediate tables with validation data"
author: "A. Lindborg"
date: "4/8/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---
# Purpose
1) Take the control data set w/calibration groups and make several intermediary summary tables. For some groups (e.g. Chaoborus), all the lifestages need to be rolled up (e.g. larvae and pupae) so there is 1 abundance value for Chaoborus per study/enclosure/date.


**This script rolls up the taxon specific data to evaluate calibration criteria at the level of consenus group**
I followed the methods outlined by Waterborne in the criteria_groups excel sheets, which are in the "Calibration documents from Waterborne" folder in the main R repo for this project.


# History
4/6/2022 - A. Lindborg modifies script based on L. Mudge Calibration script of same name

# Setup
```{r setup}
library(tidyverse)
library(openxlsx)
library(lubridate)
library(RColorBrewer)
library(imputeTS)

```

# Data
Read in the mesocosm control data & compiled calibration criteria
* For the intermediary datasets, we are interested in the critters considered for calibration (macroinverts, zooplankton, periphyton, and phytoplankton)

```{r raw_data}

## Control data: only groups considered for calibration criteria
d <- read_csv("Output/01_Compile_Control_Data/control_data_for_validation.csv")

## Calibration criteria
crit <- read.xlsx("R_Analyses/compiled_calibration_crit.xlsx",
                  sheet = "calib_crit",
                  detectDates = TRUE) %>%
  rename(crit_min = min_value,
         crit_max = max_value)

#peak_dates <- crit %>% distinct(parameter_group, consensus_group, peak_date_start, peak_date_end)

## Enclosure information
encl <- read.csv('//pfs1w/C2000-C3999/C3143_Mesocosm_Waterborne/Data/Mesocosm/GmbH_Mesocosm_Specifications.csv')


```

# 1. Sum abundances for taxa with multiple life stages - by study/enclosure, parameter_group, consensus_group, DATE

* Macroinverts - Chaoborus, Chironomidae, Tanypodinae
* Zooplankton - Diaptomidae & Cyclopidae (predatory copepods)

4/28/2021- fixed selection of Cyclopidae (had 2 spellings) - LM

```{r sum_life_stages}
# rename variables so diff life stages have the same name
# group by study, encl, param group, cons grp, var, date 
# mutate, new_val = sum(val) -- check: life stage species should still have 2 rows, see summed value; non-life stage groups new_val=Val
# then use distinct on grouping vars

d.sum <- d %>%
  mutate(variable = case_when(
         grepl("Chaoborus", variable) ~ "Chaoborus sp.",
         grepl("Chironomidae", variable) ~ "Chironomidae",
         grepl("Tanypodinae", variable) ~ "Tanypodinae",
         grepl("Diaptomidae", variable) ~ "Diaptomidae",
         grepl("Cyclopoidae", variable) ~ "Cyclopoidae", 
         grepl("Cyclopidae", variable) ~ "Cyclopoidae",
         TRUE ~ variable)) %>%
  group_by(study, enclosure, parameter_group, consensus_group, variable, date) %>%
  mutate(abund_sum_lifestage = sum(value)) %>%
  ungroup() %>%
  distinct(study, enclosure, parameter_group, consensus_group, variable, date, .keep_all = TRUE) %>%
  dplyr::select(-value)

write_csv(d.sum, "Output/02_Control_and_Calib_byGroup/sum_life_stages_bySpecies.csv")
saveRDS(d.sum, "Output/02_Control_and_Calib_byGroup/sum_life_stages_bySpecies.rds")
 
```

