---
title: "Convert Macrophyte Abundances to Biomass"
author: "A. Lindborg"
date: "4/8/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---
# Purpose
Convert macrophyte control data from percent cover to grams/m2 for comparison to Aquatox results.


# Documentation
Per internal meeting on 12/14/21, B.Sackmann stated that set limit of macrophytes in Aquatox to 100 g/m2. Therefore, for this conversion, we will set the max % cover to 100 g/m2, so for each species it's really a 1:1 for percent cover to g/m2 (ie 60% = 60 g/m2)-12/15/21

# History
4/6/2022 - A. Lindborg modifies script based on L. Mudge Calibration script of same name



# Setup
```{r setup}
library(tidyverse)
library(openxlsx)
library(janitor)
library(RColorBrewer)


options(scipen = 9999)
```

# Data
```{r data}

d.meso <- readRDS("Output/02_Control_and_Calib_byGroup/sum_life_stages_bySpecies.rds") %>% 
  filter(parameter_group == "Macrophytes") %>%
  filter(variable == "Myriophyllum spicatum" | variable == "Chara globularis") %>%
  dplyr::select(study:date2, abund_sum_lifestage)
```

# Conversion from % cover to grams/m2

```{r conversion}
#max_value = max(plants$abund_sum_lifestage) #114.4

AQ_Macrophytes <- d.meso %>%
  dplyr::select(-parameter_group, -consensus_group, -units_or_id) %>%
  rename(species_group = variable,
         group_abundance = abund_sum_lifestage) %>%
  mutate(
    #ratio = abund_sum_lifestage/max_value,
    #mass_g_per_area = ratio * 100,
    group_biomass = group_abundance,
    units_for_aquatox = "g/m2 dry",
    non_detects = 0, 
    min_bar_value = group_biomass,
    max_bar_value = group_biomass)

write.csv(AQ_Macrophytes, paste0("Output/07_Biomass_Conversions/Aquatox_Macrophyte_Overlay_", Sys.Date(), ".csv"))


```

