---
title: "Physical & Chemical Parameter Overylay File"
author: "A. Lindborg"
date: "11/30/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Purpose
Compile all physical and abiotic parameters for the Aquatox Overlay File.

+ = dataset the variable can be found in
** = No data provided by Waterborne/GmBH

Physical parameters that are AQ state variables:
  - Water volume          + Mesocosm control data
  - Temperature           + Mesocosm control data (for enclosure); + Simulated data from gaiac
  - Wind Loading          + MET data  
  - Light                 + MET data
  - pH                    + Mesocosm control data
  
Chemical Parameters that are AQ state variables:
  - Total Ammonia as N    + Mesocosm control data
  - Nitrate as N          + Mesocosm control data  
  - Total Soluble P       + Mesocosm control data
  - Carbon Dioxide**
  - Oxygen                + Mesocosm control data
  


# Documentation

# History
4/6/2022 - A. Lindborg modifies script based on L. Mudge Calibration script of same name


# Setup
```{r setup}
library(tidyverse)
library(openxlsx)
library(janitor)
library(RColorBrewer)

options(scipen = 9999)
```

# Steps
1. Load the data & filter for the variables needed

2. For water volume- convert from liters to cubic meters (units req. for Aquatox)

3. Create a mock timeseries for water level. Even though volume remains constant in each study, want a timeseries for the overlay file- just use the dates from the physical/chem parameter data

4. Combine the water vol data to the rest of the phy/chem data

**MET data will be saved separately-- these variables (light and wind) have hourly measurements, formatted with a specific way that AQ reads in DateTime stamps


# Load and organize parameters from Control Data:
```{r control_params}
# Load control Mesocosm study data -- filter for variables and clean up units:
cd <- read.csv("R_Analyses/01_Model_Validation/Output/01_Compile_Control_Data/control_long.csv") %>%
  filter(parameter_group %in% c("Chemical-Parameters", "Physical-Parameters")) %>%
  separate(variable, into=c("variable", "units"), sep=" ") %>%
  filter(variable %in% c("Nitrate", "Phosphate", "Ammonium", "Temperature", "Oxygen", "pH")) %>%
  mutate(units = case_when(
    variable %in% c("Nitrate", "Ammonium", "Phosphate", "Oxygen") ~ "mg/L",
    variable == "Temperature" ~ "deg_C"),
    date = as.POSIXct(date, format="%Y-%m-%dT%H:%M")) %>%
  dplyr::select(-units_or_id, -date2)


# specifying this is for the enclosure because we also have air temperature from weather stations
cd$variable[cd$variable == "Temperature"] <- "Temp_enclosure" 




# Water Level/ Volume -- convert from L to cubic meters; filter for studies that are in control data; remove var with liters
wl <- read_csv("Input/GmbH_Mesocosm_Specifications_copied01-17-22.csv") %>%
  janitor::clean_names() %>%
  dplyr::select(dataset_name, enclosure_water_volume_l) %>%
  mutate(value = enclosure_water_volume_l/1000,
         variable = "Water_Volume",
         units = "cubic_meters") %>%
  rename(study = dataset_name) %>%
  filter(study %in% unique(cd$study)) %>%
  dplyr::select(-enclosure_water_volume_l)

# Create a mock timeseries for water volume: 
wl.ts <- cd %>%
  distinct(study, enclosure, date) %>%
  left_join(., wl) %>%
  mutate(parameter_group = "Physical-Parameters")

```


# Load simulated water temp data from Gaiac:
```{r water_temp}
# WATER TEMPS
water.temp <- read_csv("Output/Daily_Mean_Water_Temp_2013-2019_Mesocosm_Homberg.csv") %>%
  dplyr::select(-day) %>%
  rename(value = mean_temp_deg_C,
         date=Date) %>%
  mutate(variable = "Avg_Water_Temp",
         units = "deg_C",
         date = as.Date(date),
         parameter_group = "Physical-Parameters")
```


# Combine mesocosm & simulated water temps together for an aq_overlay file:
```{r}
pc_aquatox <- bind_rows(cd, wl.ts, water.temp)
write.csv(pc_aquatox, "Output/09_Abiotic_Parameters_for_Overlay/Phys_Chem_Overlay_Data.csv")
```


# Load and organize parameters from Meterological Data:
```{r met_data}

# LIGHT
light <- read.xlsx("Output/Light_2013-2019_LangleyPerDay_all.xlsx") %>%
  dplyr::select(-Year) %>%
  rename(date = DateTime,
         value = Light_Langley_per_day) %>%
  mutate(variable = "Light",
         units = "Ly/day")

# WIND SPEED
    ## Follow methods from C3143_Weather_Data_Conversions.R to save timestamp in a format that Aquatox will read.
wind <- read.csv("Input/Weather-2013-2019_MesocosmGmbH_Station35km_RInput.csv") %>%
  janitor::clean_names() %>%
  dplyr::select(date, time, windspeed_m_s) %>%
  mutate(DateTime = as.POSIXct(as.character(paste(date, time)), format="%m/%d/%Y %H:%M:%S"),
         Time = format(DateTime, "%I:%M %p", usetz = F)) %>%
  dplyr::select(-time) %>% 
  mutate(Time = ifelse(is.na(Time), paste("12:00 AM"), Time),
         DateTime = paste(date, Time, sep = " ")) %>%
  dplyr::select(-date, -Time) %>%
  rename(value = windspeed_m_s,
         date = DateTime) %>%
  mutate(variable = "Windspeed",
         units = "m/s")

wind$value <- as.numeric(wind$value)
# Combine MET data for AQ overlay:
  ## NAs in the wind data are expected -- checked that they are missing from the raw data (which was known to have missing values from some sensor malfunctions)
  ## Save as .xlsx because the date format will change if save as .csv
met_overlay <- bind_rows(light, wind) %>%
  openxlsx::write.xlsx(., "Output/09_Abiotic_Parameters_for_Overlay/MET_Overlay_Data.xlsx")

```
