---
title: "01_Compile_Control_Data"
author: "A. Lindborg"
date: "11/30/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Purpose
Organize data from the 2021 validation control studies into one master dataset. Data are provided by GmbH.

Output = Dataframe with the following columns
  * Study: 21a.1, 21a.2
  * Parameter Group: (e.g. chemical parameters, macrophytes, phytoplankton, etc.)
  * Units or ID: if a species will be units, if a chemical/phy parameter will be study ID
  * Date: POSIXct date, all in the same format
  * Enclosure
  * Variable: Species name or chemical/physical parameter
  * Value: measurement (biomass, count, etc.)


# History
11/30/2022 - A. Lindborg creates script
4/28/2023 - A Lindborg updates script with new full dataset from Waterborne


# Setup
```{r setup}
library(tidyverse)
library(openxlsx)
library(lubridate)

```

# Data
* Original Files from Waterborne are organized by experiment & functional group (or physical parameter)
* Excel file name components are separated by an underscore: experiment _ functional group _ experiment ID


# Read in Mesocosm Control Data

```{r read_files}

# Create a path for each experiment folder (note: not using the parent folder bc we don't want the files from _read-me or _received):
path21a.1 <- "//integral-corp.com/data/C2000-C3999/C3143_Mesocosm_Waterborne/Data/Control Validation Data 2021 GmbH/Data_control_validation/Data_control_validation/3-peak"
path21a.2 <- "//integral-corp.com/data/C2000-C3999/C3143_Mesocosm_Waterborne/Data/Control Validation Data 2021 GmbH/Data_control_validation/Data_control_validation/2-appl"



# Create a list of file names:
files <- list.files(path = c(path21a.1, path21a.2),
                    pattern = "*.csv",
                    full.names = TRUE)


# Create a df that has a nested list of the species data:
control_data_list <- tibble(filename = files) %>% 
  mutate(contents = map(filename, ~read_csv(.x, col_names = FALSE, skip_empty_rows = TRUE)), 
         file_details = map_chr(contents, ~.x[[1,1]]), #first row in each file has context for the data
         header_line = map(contents, ~.x[2, ]), # pull out the header line with col names
         data_contents = map2(contents, header_line, ~slice(.x, -c(1:2)) %>% set_names(.y))) %>%
  select(-contents, -header_line, -filename) %>%
  separate(col= file_details, into = c("study", "parameter_group", "units_or_id"), sep = "_") %>% #splits file details into 3 columns
  mutate(units_or_id = 
           case_when(parameter_group == "Emerging-Insects" ~ "[Individuals/Sample]", #manually edit formatting some units
                     parameter_group == "Phytoplankton-Chl-a" ~ "ug/L",
                     parameter_group == "Periphyton-Chl-a" ~ "ug/a",
                     TRUE ~ units_or_id),
         data_contents = map(data_contents, ~janitor::remove_empty(.x))) #renaming to match other study naming conventions
         

# Send individual data frames to the environment- named by parameter group
list2env(split(x=control_data_list, f=control_data_list$parameter_group), envir=.GlobalEnv) 

```

# Clean & Arrange Master Dataset

The below chunk creates the master dataset (includes all critters, all experiments) using the individual dataframes in the environment. The `Water-Level` and `Sediment-Water-Parameters` are not included in this data cleaning step because they have a different format than the rest of the data (and we don't need these right away)

```{r master_df}

# get a list of data frames- but first remove ones we don't need first (rm= remove)
#rm(dw)
rm(control_data_list)
rm(`Sediment-Water-Parameters`)
rm(`Water-Level`)
df_list <- Filter(function(x) is(x, "data.frame"), mget(ls()))


# Iterate over a list of data frames:
  # unnest the data_contents
  # pivot_longer
  # filter out any NA from value (so we aren't keeping empty rows)
  # remove < symbol from values
  # convert "value" to numeric class
  # Fix Date column- put into standard format
  # bind all data together

out <- c()

for(i in seq(1:length(df_list))){
  tmp <- df_list[[i]] %>%
    unnest(cols=c(data_contents)) %>%
    pivot_longer(cols=!c(study:Enclosure), names_to = "Variable", values_to = "Value") %>%
    filter(!is.na(Value)) %>%
    mutate(Value = as.numeric(gsub("<", "", Value)),
           Date = lubridate::parse_date_time(x=Date, orders = c("d-b-y"), tz = "UTC"),
           date2= Date) # created 2ndary date column so can set all years to be the same, below
  
  out <- bind_rows(out, tmp)
  
  
}

lubridate::year(out$date2) <- 2022
out <- janitor::clean_names(out)

write_csv(out, "Output/01_Compile_Control_Data/control_long_2021.csv")
saveRDS(out, file = "Output/01_Compile_Control_Data/control_long.rds")


# Try removing the unicode replacement symbol (black triangle with question mark)
#out$Variable <- enc2utf8(out$Variable)
#out$Variable <- gsub("/uFFFD", "", out$Variable, fixed=TRUE)
#out$Variable <- gsub("/u00B0", "", out$Variable, fixed=TRUE)

```
# Subset data with calibration criteria
The purpose of this section is to create a subset output data file that only contains data for the groups that have calibration criteria- this is so that for future plots, etc. we don't have to repeat the filtering.

Calibration Documents from Waterborne (see folder by same name in R_analyses)
* `Criteria_ModelCalib_4Mar2021.docx` -- summary of all consensus groups
* `criteria_groups_M_Z_03Mar2021.xlsx` -- zooplankton and macroinvertebrates methods (incl. how individual species grouped)
* `criteria_groups_phyto_peri_3Mar2021.xlsx` -- phytoplankton and periphyton methods
* `ControlGraphs_2021-01-28.docx` -- ref that explains which life stages are added together for a total abundance per date

```{r calib_data}

# Calibration criteria -- DO NOT MOVE EARLIER IN SCRIPT, will mess up creation of "out"
crit <- read.xlsx("//integral-corp.com/data/C2000-C3999/C3143_Mesocosm_Waterborne/Working_Files/R_Analyses/compiled_calibration_crit.xlsx", sheet = "calib_crit", detectDates = TRUE) %>%
  rename(crit_min = min_value,
         crit_max = max_value)

# Add Macrophytes to the crit dataset- not part of the official calibration criteria, but important for modeled groups!
macro <- out %>% filter(parameter_group == "Macrophytes") %>% distinct(parameter_group, variable, units_or_id) %>% rename(units=units_or_id)
crit <- bind_rows(crit, macro)

# Subset data
dsub <- semi_join(out, crit, by = c("parameter_group", "variable"))

#Check that the groups/species match EXACTLY between dsub and criteria:
ct <- crit %>% distinct(parameter_group, variable) %>% arrange(parameter_group, variable)
dt <- dsub %>% distinct(parameter_group, variable) %>% arrange(parameter_group, variable)

dplyr::all_equal(ct, dt) #TRUE
rm(ct)
rm(dt)

# Add consensus group
#dc <- left_join(dsub, crit %>% select(parameter_group, consensus_group, variable), by = c("parameter_group", "variable"))
dc <- left_join(dsub, crit, by = c("parameter_group", "variable")) %>%
  relocate(enclosure, .after = study) %>%
  relocate(c(consensus_group, variable), .after = parameter_group) %>%
  relocate(date2, .after = date) %>%
  dplyr::select(-units) #redundant
  
write_csv(dc, "Output/01_Compile_Control_Data/control_data_for_validation.csv")
saveRDS(dc, "Output/01_Compile_Control_Data/control_data_for_validation.rds")

```

