---
title: "Create Aquatox Overlay File"
author: "A. Lindborg"
date: "11/30/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Purpose
Compile all the converted mesocosm control data into an overlay file for AQUATOX.

*Currently not QA'd, for internal purposes only- this will format the biomass data for Brandon to upload into Aquatox*


## Workflow Notes:
1. Keep same ordering (i.e. sheet numbering and names) so it matches our documentation in SmartSheet and allows B.Sackmann to easily ID and upload the files to Aquatox (manual process).
2. The summary statistics tab should remain un-numbered at the end (for senior review)
3. Update the "df_update" to document what sheets were changed and summary of the changes.
4. Whenever a new overlay file is uploaded to SmartSheets, analysts should log into SmartSheet and edit the file description to include a list of exactly WHICH tabs were modified, so B.Sackmann knows which ones to update in Aquatox.


# Documentation
Must follow format specified by B. Sackmann in email. *ADD LINK

we just need simple XLS worksheets (one sheet per species/variable)…or a XLS workbook with separate tabs for each species

# History
11/30/2022 - A. Lindborg creates file


# Setup
```{r setup}
library(tidyverse)
library(openxlsx)
library(janitor)
library(RColorBrewer)

# For uploading file to SmartSheet:
source("Input/rsmartsheet_functions_revised.R")
library(httr)


options(scipen = 9999)
```

# Data
* Note: analyst should archive files based on the date. One file per group should be retained in the Output folder, whichever has most recent date.
** If updates were made to biomass conversions, will need to update the file path use the most recent file!!
```{r data}
macroinvert <- read_csv("Output/07_Biomass_Conversions/Aquatox_Macroinvert_Overlay_2023-05-19.csv")
macrophyte <- read_csv("Output/07_Biomass_Conversions/Aquatox_Macrophyte_Overlay_2023-05-19.csv")
zooplank <- read_csv("Output/07_Biomass_Conversions/Aquatox_zooplankton_Overlay_2023-05-19.csv")
periphyt <- read_csv("Output/07_Biomass_Conversions/Aquatox_PeriPhyto_Overlay_2023-05-19.csv")
phys <- read_csv("Output/09_Abiotic_Parameters_for_Overlay/Phys_Chem_Overlay_Data.csv")
met <- openxlsx::read.xlsx("Output/09_Abiotic_Parameters_for_Overlay/MET_Overlay_Data.xlsx")


# Combine all the biomass data together:
d <- bind_rows(macroinvert, macrophyte, zooplank, periphyt) 



```

```{r save_combined_biomass}

# Save a reference dataframe that is just the biomass data from all groups:
cd <- d %>%
  dplyr::select(study, enclosure, parameter_group, date, units_for_aquatox, species_group, group_biomass) %>%
  mutate(parameter_group = case_when(
    !is.na(parameter_group) ~ parameter_group,
    is.na(parameter_group) & species_group %in% c("Chara globularis", "Myriophyllum spicatum")  ~ "Macrophytes",
    is.na(parameter_group) & grepl("Peri", species_group ) ~ "Periphyton-Chl-a",
    is.na(parameter_group) & grepl("Phyto", species_group) ~ "Phytoplankton-Chl-a",
    is.na(parameter_group) & species_group %in% c("Cladocera_phytophilous", "Rotifera_herbivorous1", "Cladocera_small", "Copepoda_predatory", "Daphnidae", "Copepoda_herbivorous", "Rotifera_herbivorous2", "Simocephalus") ~ "Zooplankton",
    TRUE ~ NA_character_
  ),
  
  consensus_group = case_when(
    species_group == "Total Periphyton" ~ "Total Periphyton",
    species_group == "Total Phytoplankton" ~ "Total Phytoplankton",
    parameter_group %in% c("Periphyton-Chl-a", "Phytoplankton-Chl-a") ~ sub(".*? ", "", species_group), # doesn't override the total assignments above
    species_group %in% c("Anisoptera", "Zygoptera") ~ "Odonata",
    TRUE ~ species_group
  )) %>%
  rename(biomass=group_biomass)

write_csv(cd, "Output/07_Biomass_Conversions/all_control_data_in_biomass.csv")


# https://stackoverflow.com/questions/32767164/use-gsub-remove-all-string-before-first-white-space-in-r
```


To do for cleanup & write out:
-remove x column
-rename columns to match names specified in Brandon's email
-reorder columns to match order specified in Brandon's email - with additional ones at the end
-Create an order column to preserve order for when we have to update with more variables
-Create a workbook, split tabs based on species/parameter
    - First write out biomass data, then add on physical parameters & MET data
    - Keeping biomass data separate because phys/met data have different column names and MET data has a unique date format.
```{r create_overlay_dataframes}
## FORMAT BIOMASS DATA:
aq_overlay <- d %>%
  dplyr::select(-`...1`, -date2) %>% # first col might be called X1 or ...1
  relocate(c(group_biomass, non_detects, min_bar_value, max_bar_value), .after = "date") %>%
  relocate(c(group_abundance, group_encl_abundance, units_for_aquatox, study, enclosure), .after="max_bar_value") %>%
  mutate(Empty = "") %>%
  relocate(Empty, .after = max_bar_value) %>%
  rename(Date = date,
         Data = group_biomass,
         `Non-detects`= non_detects,
         `Min-bar value`= min_bar_value,
         `Max-bar value` = max_bar_value,
         `Sample Counts` = group_abundance,
         `Enclosure Extrapolation`= group_encl_abundance,
         `Final Units` = units_for_aquatox,
         Study= study,
         Enclosure = enclosure) %>%
  mutate(Date = format(Date, format= "%m/%d/%Y")) %>%# Must be in this format for upload to Aquatox- LM
         #Date_2021=format(Date_2021, format= "%m/%d/%Y"))
  arrange(parameter_group, species_group, Date) %>%
  dplyr::select(-parameter_group)


# SET SPECIES ORDER FOR BIOMASS DATA:  
  # Split the AQ overlay-- original vs. newly added, this way we keep tacking tabs on at the end and don't mess up the ordering:

  # This is the original: need to filter out "new" records
aq_overlay1 <- aq_overlay %>% 
  filter(!species_group %in% c("Total Periphyton", "Total Phytoplankton", "Hirudinea"))  %>% # REMOVE ANY "NEW" RECORDS HERE
  mutate(order = ordered(species_group, levels = c("Anisoptera", "Asellus", "Chaoborus", "Chironomidae", "Cloeon", "Gammarus" ,
                                                  "Gastropoda", "Nepomorpha", "Oligochaeta", "Tanypodinae" , "Zygoptera" , "Chara globularis",
                                                  "Cladocera_phytophilous","Cladocera_small","Copepoda_herbivorous","Copepoda_predatory","Daphnidae",
                                                  "Myriophyllum spicatum", "Rotifera_herbivorous1","Rotifera_herbivorous2","Simocephalus",
                                                  "Peri Blue Greens","Peri Diatoms", "Peri Greens","Phyto Blue Greens","Phyto Cryptophytes",
                                                  "Phyto Diatoms", "Phyto Greens")))

  # This is any groups added after the original already created: Add them onto the end of the list (i.e. newest species is last in order)
aq_overlay2 <- aq_overlay %>% 
  filter(species_group %in% c("Total Periphyton", "Total Phytoplankton", "Hirudinea")) %>% # KEEP ANY "NEW" RECORDS
  mutate(order = ordered(species_group, levels = c("Total Periphyton", "Total Phytoplankton", "Hirudinea")))

## FORMAT SUMMARY STATS:
aq_sum_stats1 <- aq_overlay1 %>%
  group_by(order, `Final Units`) %>%
  #mutate(sheet_name = )
  summarize(`Initial Condition (5th Percentile of Non-zero Values)` = quantile(Data[Data>0], 0.05), # initial condition, as defined by B.Sackmann (5th percentile of non-zero values)
            Min = min(Data),
            Max = max(Data),
            Median = median(Data),
            Average = mean(Data, na.rm=TRUE)) %>%
  ungroup() %>%
  mutate(order_no = 1:n(),
         sheet_name = paste0(order_no, "_", order)) %>%
  dplyr::select(-order, -order_no) %>%
  relocate(sheet_name, .before = `Final Units`)

aq_sum_stats2 <- aq_overlay2 %>%
  group_by(order, `Final Units`) %>%
  #mutate(sheet_name = )
  summarize(`Initial Condition (5th Percentile of Non-zero Values)` = quantile(Data[Data>0], 0.05), # initial condition, as defined by B.Sackmann (5th percentile of non-zero values)
            Min = min(Data),
            Max = max(Data),
            Median = median(Data),
            Average = mean(Data, na.rm=TRUE)) %>%
  ungroup() %>%
  mutate(order_no = 1:n(),
         #sheet_name = paste0(order_no, "_", order)) %>%
         sheet_name = paste0(order)) %>% # numbers won't match bc these were put on at the very end.
  dplyr::select(-order, -order_no) %>%
  relocate(sheet_name, .before = `Final Units`)

aq_sum_stats <- bind_rows(aq_sum_stats1, aq_sum_stats2)


## FORMAT PHYSICAL DATA
aq_phys <- phys %>%
  dplyr::select(-`...1`, -parameter_group) %>% # first col might be X1 or ...1
  rename(Date = date,
         Study= study,
         Enclosure= enclosure,
         Variable = variable,
         Data= value,
         `Final Units` = units) %>%
  mutate(`Non-detects` = NA,
         `Min-bar value` = Data,
         `Max-bar value` = Data,
         Empty = "",
         Date = format(Date, format= "%m/%d/%Y"), # Must be in this format for upload to Aquatox- LM
         order = ordered(Variable, levels = c("Ammonium", "Nitrate", "Phosphate", "Temp_enclosure", "Avg_Water_Temp", "Water_Volume", "Oxygen", "pH"))) %>%
  relocate(Date, Data, `Non-detects`, `Min-bar value`, `Max-bar value`, Empty, .before = Study)

## FORMAT MET DATA
aq_met <- met %>%
  rename(Date = date,
         Data = value,
         Variable = variable,
         `Final Units` = units) %>%
  mutate(`Non-detects` = NA,
         `Min-bar value` = Data,
         `Max-bar value` = Data,
         Empty = "",
         order = ordered(Variable, levels = c("Light", "Windspeed"))) %>%
  relocate(`Non-detects`, `Min-bar value`, `Max-bar value`, Empty, .before = Variable)


rm(aq_overlay)

```

```{r ADD_UPDATE_NOTES}
## FORMAT DOCUMENTATION: ANALYST SHOULD POPULATE EACH TIME SOMETHING IS CHANGED
updated_sheets <- c("41_Hirudinea")

df_update <- data.frame(updated_sheets) %>%
  mutate(date = Sys.Date(),
         notes = case_when(
           updated_sheets == "41_Hirudinea" ~ "Add Hirudinea sheet."
           # updated_sheets %in% c("22_Peri Blue Greens", "23_Peri Diamtoms", "24_Peri Greens") ~ "Biomass values multiplied by 4.35x scaling factor to account for walls of enclosures.",
           # updated_sheets %in% c("39_Total Periphyton", "40_Total Phytoplankton") ~ "Newly added. Each is the sum of the individual species biomass of that group. Periphyton already includes scaling factor."
           ),
         initials = "L. Mudge")
```


# Save Workbook
*SUGGSION: If making major changes, suggest adding "_TEST" to the file path in the saveWorkbook() call and reviewing the workbook before overwriting the existing one- Lm
```{r save_workbook}


# Save a workbook, one tab per species:
  # This package only saves .xlsx files, even if change the extension. Will manually open and save .xlsx to .xls for AQUATOX
wb <- createWorkbook()
n <- 0

# Write out Biomass Data -- 28 species (as of 1/17/2022)
for(i in seq_along(levels(aq_overlay1$order))) {
  
  sp <- levels(aq_overlay1$order)[i] # Get the species name based on the order
  sub <- aq_overlay1 %>% filter(species_group==sp) %>% dplyr::select(-species_group, -order) # filer the data
  
  addWorksheet(wb, sheetName=paste(i, sp, sep="_"))
  writeData(wb, sheet=paste(i, sp, sep="_"), x=sub , colNames = TRUE)
  
}

# Write out Physical Parameter Data
for(i in seq_along(levels(aq_phys$order))) { 
  
  n <- i + 28 # Add 28 since that is where prev records stopped
  var <- levels(aq_phys$order)[i] # Get the species name based on the order
  sub <- aq_phys %>% filter(Variable==var) %>% dplyr::select(-Variable, -order) # filer the data
  
  addWorksheet(wb, sheetName=paste(n, var, sep="_"))
  writeData(wb, sheet=paste(n, var, sep="_"), x=sub , colNames = TRUE)
}

# Write out MET data:
for(i in seq_along(levels(aq_met$order))) { 
  
  n <- i +36
  var <- levels(aq_met$order)[i] # Get the species name based on the order
  sub <- aq_met %>% filter(Variable==var) %>% dplyr::select(-Variable, -order) # filer the data
  
  addWorksheet(wb, sheetName=paste(n, var, sep="_"))
  writeData(wb, sheet=paste(n, var, sep="_"), x=sub , colNames = TRUE)
}

# Write out NEW ADDITIONS:
for(i in seq_along(levels(aq_overlay2$order))) {
  n <- i + 38 # Add 38 since that was last numbered tab on 1/25/2022 AQ overlay file
  sp <- levels(aq_overlay2$order)[i] # Get the species name based on the order
  sub <- aq_overlay2 %>% filter(species_group==sp) %>% dplyr::select(-species_group, -order) # filer the data
  
  addWorksheet(wb, sheetName=paste(n, sp, sep="_"))
  writeData(wb, sheet=paste(n, sp, sep="_"), x=sub , colNames = TRUE)
}


# Write out Summary Stats table:
addWorksheet(wb, sheetName="Biomass_Summary_Stats")
writeData(wb, sheet="Biomass_Summary_Stats", x=aq_sum_stats , colNames = TRUE)


# Write out Updates table:
addWorksheet(wb, sheetName="Updates")
writeData(wb, sheet="Updates", x=df_update , colNames = TRUE)

#saveWorkbook(wb, paste0("Output/07_Biomass_Conversions/aquatox_overlay_data_", sys.date.f, ".xlsx"), overwrite = TRUE)
saveWorkbook(wb, paste0("Output/08_Aquatox_Overlay_Data/aquatox_overlay_data.xlsx"), overwrite = TRUE)



#Original loop used
#sys.date.f <- format(Sys.Date(),"%Y%m%d")

# for(i in unique(aq_overlay$species_group)) {
#   n <- n + 1
#   addWorksheet(wb, sheetName=paste(n, i, sep="_"))
#   writeData(wb, sheet=paste(n, i, sep="_"), x= aq_overlay%>%filter(species_group==i) %>%dplyr::select(-species_group), colNames = TRUE)
# }
```


# Upload AQUATOX overlay file to SmartSheet

*Before running code below: You must save the .xlsx above, then manually open and re-save as .xls file.*

* If uploading an attachment for the first time, must be done manually on SmartSheet, this is to *replace* an attachment with an updated file
* Updated file name must match attachment file name

```{r update_smartsheet_attachment}
set_smartsheet_api_key("bfwur1znl9z5cdlr101msb1s2r")

# REPLACE SHEET ATTACHMENT
  # Has 3 arguments: sheet_name, file_path, attachment_name
replace_sheet_attachment(sheet_name = "Control Data Conversion Tracking", 
                         file_path = "Output/08_Aquatox_Overlay_Data/aquatox_overlay_data.xls",
                         attachment_name = "aquatox_overlay_data.xls")
```

